---
title: "Group Differences"
output: "Compare Conditions"
---

# Libraries

```{r include=FALSE}
require(tidyverse)
require(sjstats)
```
# Data

```{r}
group_df <- read_csv("data/group_level_data.csv")
indiv_df <- read_csv("data/indiv_level_data.csv")
memory_df <- read_csv("data/memory_test_data.csv")
```
# Cleaning

## drop additional groups

```{r}
group_df <- group_df %>% 
  filter(!group %in% c(14, 80))

indiv_df <- indiv_df %>% 
  filter(!group %in% c(14, 80))

memory_df <- memory_df %>% 
  filter(!group %in% c(14, 80))
```
## convert to binary decision

```{r}
group_df <- group_df %>%
  mutate(binary_decision = decision == "C") %>% 
  mutate(binary_decision_numeric = binary_decision * 1)
```
## add columns for TMS (yes/no) and group structure (h/so)

```{r}
group_df <- group_df %>%
  separate(condition, c('group_structure','TMS'), sep = '_', remove = FALSE)
```
# Compare conditions

## number of correct decisions overall

```{r}
group_df
group_df %>% 
  filter(decision == "C") %>% 
  count()/80 * 100
  
group_df %>% 
  filter(binary_decision == TRUE) %>% 
  nrow()

 group_df %>% 
  summarise(percent_correct = sum(binary_decision_numeric)/n() * 100)
```
## run chi-square tests to compare conditions

```{r}
chisq.test(group_df$binary_decision, group_df$group_structure)

group_df %>%
  group_by(TMS) %>%
  summarise(mean(binary_decision))

group_df %>%
  group_by(group_structure) %>%
  summarise(mean(binary_decision * 1))

group_df %>%
  group_by(group_structure, TMS) %>%
  summarise(mean(binary_decision))

chisq.test(group_df$binary_decision, group_df$TMS)
```
## plot correct decisions by manipulations

```{r}
ggplot(data = group_df, aes(TMS, binary_decision_numeric)) +
  stat_summary(fun.y = "mean", geom = "bar") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar")
```


```{r}
ggplot(data=group_df, aes(group_structure, binary_decision_numeric)) +
  stat_summary(fun.y = "mean", geom = "bar") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar")
```


```{r}
require(Hmisc)

ggplot(data=group_df, aes(condition, binary_decision_numeric)) +
  stat_summary(fun.y = "mean", geom = "bar") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar")


## for plot 

plot_data <- group_df %>%
  group_by(condition, group_structure, TMS) %>%
  mutate(pct = mean(binary_decision_numeric))

plot_data

ggplot(data=plot_data, aes(condition, binary_decision_numeric, label = scales::percent(pct))) +
  stat_summary(fun.y = "mean", geom = "bar") +
  labs(x = "Condition", y = "Percentage of Correct Decisions") +
  ylim(0, 1) +
  geom_text(aes(label = scales::percent(pct), 
                  y = pct, 
                  group = condition),
              position = position_dodge(width = 0.9),
              vjust = -0.8)
  
```

```{r}
plot_data
pd <- plot_data %>%
  group_by(condition, group_structure, TMS) %>% 
  summarise(correct_percentage = mean(binary_decision_numeric))


ggplot(data=pd, aes(group_structure, correct_percentage, fill = TMS)) +
  geom_bar(stat="identity", position="dodge2") +
  labs(x = "Group Structure", y = "Percentage of Correct Decisions") +
  ylim(0, 1) +
  scale_x_discrete(labels = c('Hierarchical', 'Self-organized')) +
  scale_fill_manual(values = c("#003f5c", "#ffa600"), labels = c('Without', 'With')) +
  #scale_fill_brewer(palette="Spectral", labels = c('Without', 'With')) +
  geom_text(aes(label = scales::percent(correct_percentage), 
                  y = correct_percentage),
              position = position_dodge(width = 0.9),
              vjust = -1)
```

## logistic regression to look at interaction of TMS and group structure
```{r}
simpleTMS <- glm(binary_decision ~ TMS, data = group_df, family = 'binomial'); summary(simpleTMS)

full_additive_model <- glm(binary_decision ~ TMS + group_structure, data = group_df, family = 'binomial'); summary(full_additive_model)

confint(full_additive_model, level = 0.95) # 95% Confidence Intervalls
exp(coef(full_additive_model)) # Odds Ratios

fullmodel <- glm(binary_decision ~ TMS * group_structure, data = group_df, family = 'binomial'); 
summary(fullmodel)

confint(fullmodel, level = 0.95) # 95% Confidence Intervalls
exp(coef(fullmodel)) # Odds Ratios


anova(full_additive_model, fullmodel, test="Chisq") # model comparison
```
## logistic regression to check whether duration of discussion is predictive

```{r}
time_model <- glm(binary_decision ~ duration_min, data = group_df, family = 'binomial'); summary(time_model)

time_model_TMS <- glm(binary_decision ~ TMS + duration_min, data = group_df, family = 'binomial'); summary(time_model_TMS)

time_model_interact <- glm(binary_decision ~ TMS * duration_min, data = group_df, family = 'binomial'); summary(time_model_interact)

time_hierarchy_interact <- glm(binary_decision ~ duration_min * group_structure, data = group_df, family = 'binomial'); summary(time_hierarchy_interact)

time_all_model <- glm(binary_decision ~ duration_min + group_structure + TMS, data = group_df, family = 'binomial'); summary(time_all_model)

confint(time_all_model)
exp(coef(time_all_model))

anova(full_additive_model, time_all_model, test = "Chisq")
```
### what predicts duration?

```{r}
# change independent variables to factors
group_df_factor <- group_df %>% 
  mutate(TMS = as.factor(TMS), group_structure = as.factor(group_structure))

time_hierarchy <- lm(duration_min ~ group_structure, data = group_df_factor); summary(time_hierarchy)

time_predict <- lm(duration_min ~ TMS * group_structure, data = group_df_factor) 
summary(time_predict)

require(reghelper)

reghelper::beta(time_predict, na.rm = TRUE)

aov_model <- aov(duration_min ~ TMS * group_structure, data = group_df); summary(aov_model)
eta_sq(aov_model, partial = TRUE)

t.test(duration_min ~ group_structure, data = group_df)

group_df %>%
  group_by(condition) %>%
  summarise(m = mean(duration_min), v = sd(duration_min))

group_df %>%
  group_by(group_structure) %>%
  summarise(m = mean(duration_min), v = sd(duration_min))
```
### duration's affect on outcome

```{r}
# in the self-organized condition, does time predict outcome?
time_hierarchy_TMS <- glm(binary_decision ~ duration_min - 1 , data = group_df %>%
                            filter(group_structure == 'so'), family = 'binomial'); summary(time_hierarchy_TMS)

# in the hierarchical condition, does time predict outcome?
time_hierarchy_TMS <- glm(binary_decision ~ duration_min - 1 , data = group_df %>%
                            filter(group_structure == 'h'), family = 'binomial'); summary(time_hierarchy_TMS)
```
### plot duration and outcome

```{r}
ggplot(group_df, aes(duration_min, binary_decision * 1)) +
  geom_point() +
  geom_smooth()
```
### see if excluding outliars does anything

```{r}
time_hierarchy_TMS <- glm(binary_decision ~ duration_min - 1, data = group_df %>% 
                            filter(duration_min < 31), family = 'binomial'); summary(time_hierarchy_TMS)
```