---
title: "Descriptive Statistics"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Libraries

```{r}
library(readr)
library(tidyverse)
library(forcats)
library(psych)
library(broom)
require(sjstats)
```
# Load data

```{r}
group_df <- read_csv("data/group_level_data.csv", col_types = cols(
  condition = col_factor(levels = NULL),
  pilot_profile = col_factor(levels = NULL),
  decision = col_factor(levels = NULL),
  location = col_factor(levels = NULL),
  familiarity = col_factor(levels = NULL)
  ))

indiv_df <- read_csv("data/indiv_level_data.csv", col_types = cols(
  `leader?` = col_factor(levels = NULL),
  gender = col_factor(levels = NULL),
  discipline = col_factor(levels = NULL),
  `formal_leader?`= col_factor(levels = NULL),
  indiv_decision = col_factor(levels = NULL),
  `final_decision?` = col_factor(levels = NULL),
  `exp_p1?` = col_factor(levels = NULL),
  `exp_p2?` = col_factor(levels = NULL),
  `exp_p3?` = col_factor(levels = NULL),
  bias = col_factor(levels = NULL)
  ))

memory_df <- read_csv("data/memory_test_data.csv",
                      col_types = cols(
                        pilot = col_factor(levels = NULL)
                        ))
                      
shared_unshared_df <- read_csv("data/shared_unshared_inf.csv",
                               col_types = cols(
                                 pilot = col_factor(levels = NULL)
                                 ))

```
# Data cleaning 

```{r}
# check how many groups per condition

group_df %>% 
  group_by(condition) %>% 
  count()

indiv_df %>% nrow()

# remove the two additional groups from h_noTMS, no.14 and no.80 due to changed version of the task

group_df <- group_df %>% 
  filter(!group %in% c(14, 80))

indiv_df <- indiv_df %>% 
  filter(!group %in% c(14, 80))

memory_df <- memory_df %>% 
  filter(!group %in% c(14, 80))

shared_unshared_df <- shared_unshared_df %>% 
  filter(!group %in% c(14, 80))

# check conditions again

group_df %>% count(condition)
```
# Basic descriptive analyses

## total sample
```{r}
indiv_df %>% 
  group_by(group, id) %>% 
  nrow()
```
## gender

### number of female and male participants

```{r}
gender_dist <- indiv_df %>% 
  count(gender)
gender_dist
```
### percentage of female and male participants 

```{r}
gender_perc <- indiv_df %>% 
  mutate(`female?` = gender == "female") %>% 
  dplyr::select(`female?`, everything())
gender_perc  

gender_perc %>% 
  summarise(percent_women = sum(`female?`)/n() * 100)
```
### explore distribution of leaders by gender

```{r}
indiv_df %>% 
  group_by(gender, `leader?`) %>% 
  count()

group_df %>% 
  filter(duration_min > 40)
```
### percentage of female/male leaders in reference to total sample

```{r}
indiv_df %>% 
  group_by(gender) %>%
  mutate(`leader?` = `leader?` == "yes") %>% 
  summarise(percent_leader = sum(`leader?`)/nrow(indiv_df) * 100)
```
### percentage of female/male leaders in reference to all leaders

```{r}

leader_percentage <- indiv_df %>% 
  mutate(`leader?` = `leader?` == "yes") %>%
  filter(`leader?` == 1) 

leader_percentage %>% 
  group_by(gender, `leader?`) %>% 
  summarise(percent_leader = sum(`leader?`)/nrow(leader_percentage) * 100)
```
### Pearson's Chi-squared test of independece: gender, leaders

```{r}
# using baseR "table"

tb <- table(indiv_df$gender, indiv_df$`leader?`)
chisq.test(tb)

# => p-value = 0.25, not significant, which means that gender and leader status are independent 
# => no biased selection
```
### gender distribution by condition

```{r}
# skinny dataframe
gender_per_condition <- indiv_df %>% 
  dplyr::select(group:number_semester)

# join with group data to add 'condition'
gender_per_condition <- gender_per_condition %>%
  left_join(group_df, by = "group")  

# explore distribution of male leaders across conditions
gender_per_condition %>% 
  filter(gender == "male") %>% 
  group_by(condition, gender) %>% 
  count()
```

### Pearson's Chi-squared test of independece: gender, condition

```{r}
test_table <- table(gender_per_condition$condition, gender_per_condition$gender)
chisq.test(test_table)

# => gender and condition are independent
```
### look at group structure (hierarchical vs. self-organized) independently

```{r}
gender_per_structure <- gender_per_condition %>% 
  separate(condition, into = c('group_structure','TMS'), sep = '_', remove = FALSE) %>% 
  group_by(group_structure, gender) %>% 
  count()

gender_per_structure
```
## age 

### average age of sample

```{r}
indiv_df %>% summarise(avg_age = mean(age, na.rm = TRUE))
summary(indiv_df$age)
sd(indiv_df$age)
```
### control for age (leaders vs. members)

```{r}
leader_yes <- indiv_df$age[indiv_df$`leader?` == 'yes']
leader_no <- indiv_df$age[indiv_df$`leader?` == 'no']

t.test(leader_yes, leader_no)

# => no signficant difference between leaders' and members' age
```
### control for age differences between conditions

```{r}
age_across_conditions <- indiv_df %>% 
  dplyr::select(group:number_semester)

age_across_conditions <- age_across_conditions %>% 
  left_join(group_df, by = "group")

# explore age distribution
age_across_conditions %>% 
  group_by(condition) %>% 
  summarise(age_by_condition = mean(age, na.rm = TRUE))

levels(age_across_conditions$condition)

# testing with ANOVA
aov_age <- aov(age ~ condition, data = age_across_conditions)
summary(aov_age)

eta_sq(aov_age, partial = TRUE)

# testing with linear regression                                  
regression_way <- lm(age ~ condition, data = age_across_conditions)
summary(regression_way)

# => no significant difference in age between conditions
```
## field of study

```{r}
# explore
ggplot(data = indiv_df, mapping = aes(discipline)) +
  geom_bar() +
  coord_flip()

indiv_df %>% 
  mutate(discipline = discipline %>% 
           fct_infreq() %>% 
           fct_rev()) %>%
  ggplot(aes(discipline)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90))

indiv_df %>% 
  count(discipline) %>% 
  arrange(desc(n))

# change factor structure to collapse into less disciplines
discipline_concise <- indiv_df %>% 
  mutate(field_of_study = fct_collapse(discipline, 'Psychology' = 'psychology', "Educational Science" = 'educational science', "Teacher's Training" = c("teacher's training", "special education"), 'Law' = c("law", "international law"), "Business & Economics" = c("economics", "management"), 'Medicine' = c("medicine", "ecotrophology"), 'Engineering' = c("engineering", "constructional engineering"), 'Applied Social Sciences' = c("criminology", "political science", "media science", "social work",'sport science'), 'Humanities' = c("philosophy", "linguistics", "history", "anthropology", "archeology"), 'Natural Sciences' = c("biology", "chemistry", "physics", "mathematics"), "Computer Science" = 'computer science')) 

discipline_concise %>% 
  count(field_of_study) %>% 
  arrange(desc(n))

# show collapsed factor as bar chart                                                             
discipline_concise %>% 
  mutate(discipline = field_of_study %>% 
           fct_infreq()) %>% 
  ggplot(aes(discipline)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90))

discipline_concise %>% 
  mutate(discipline = field_of_study %>%
           fct_relevel("Psychology", "Educational Science", "Teacher's Training", "Business & Economics", "Law", "Medicine", "Computer Science", "Engineering", "Humanities", "Applied Social Sciences", "Natural Sciences")) %>% 
  ggplot(aes(discipline)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90))

discipline_concise %>% 
  mutate(discipline = field_of_study %>% 
           fct_relevel("Psychology", "Educational Science", "Teacher's Training", "Business & Economics", "Law", "Medicine", "Computer Science", "Engineering", "Mathematics", "Humanities", "Applied Social Sciences", "Natural Sciences") %>% fct_rev()) %>%   
  ggplot(aes(discipline)) +
  geom_bar() +
  coord_flip()

# change factor order: biggest single groups first and then collapsed ones
discipline_compact <- discipline_concise %>% 
  mutate(discipline = field_of_study) %>% 
  count(discipline)

discipline_compact 

# provide percentage for each field of study
discipline_compact <- discipline_compact %>%
  mutate(percent = n/sum(n)*100) 

discipline_compact

discipline_compact %>% 
  mutate(discipline = discipline %>% 
           fct_relevel("Psychology", "Educational Science", "Teacher's Training", "Business & Economics", "Law", "Medicine", "Computer Science", "Engineering", "Humanities", "Applied Social Sciences", "Natural Sciences") %>% 
           fct_rev()) %>%
  ggplot(aes(discipline, percent)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_brewer(palette = "Blues") +
  xlab("Discipline") +
  ylab("%") 
  
indiv_df %>% 
  mutate(field_of_study = fct_lump(discipline, n = 10)) %>% 
  count(field_of_study, sort = TRUE) %>% print(n = Inf) 
```
## study experience 

### average number of semesters across sample

```{r}
indiv_df %>% 
  summarise(avg_number_semester = mean(number_semester))

# using the "psych" package for descriptive statistics on continuous variables (function "describe")
descript_stats_on_variables <- c("age", "number_semester")
describe(indiv_df[descript_stats_on_variables])
```
### control for difference in experience between leaders and members

```{r}
indiv_df %>% do(tidy(t.test(number_semester ~ `leader?`, data = indiv_df)))

# => not significant
```
### control for difference in experience between conditions

```{r}
# create the right data frame
experience_across_conditions <- indiv_df %>% 
  dplyr::select(group:number_semester)

experience_across_conditions <- experience_across_conditions %>% 
  left_join(group_df,  by = "group")

# test for significance
aov_discipline <- aov(number_semester ~ condition, data = experience_across_conditions)
eta_sq(aov_discipline, partial = TRUE)

# => not significant
```

