---
title: "Manipulation Checks"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Libraries

```{r}
library(readr)
library(tidyverse)
library(forcats)
library(psych)
require(lsr)
```
# Load in data

```{r}
group_df <- read_csv("data/group_level_data.csv")
indiv_df <- read_csv("data/indiv_level_data.csv")
```
# Clean data

```{r}
group_df <- group_df %>% 
  filter(!group %in% c(14, 80))

indiv_df <- indiv_df %>% 
  filter(!group %in% c(14, 80))
```
## create new data frame

```{r}
manip_checks <- indiv_df %>% 
  left_join(group_df, by = "group")

manip_checks <- manip_checks %>% 
  separate(condition, c('group_structure','TMS'), sep = '_', remove = FALSE)

manip_checks <- manip_checks %>% 
  mutate(binary_decision = decision == "C")

View(manip_checks)
```
# First check: Did a formal leader exist?

```{r}
manip_checks %>% 
  filter(!`formal_leader?` == "correct")
# => one person did not comply 
```
# Second check: Who made the final decision?

```{r}
manip_checks %>% 
  select(group_structure, `final_decision?`) %>% 
  filter(group_structure == "so", `final_decision?` == "leader") 
# => everyone in the self-organized condition agreed that the group made the decision

manip_checks %>% 
  select(group_structure, `final_decision?`) %>% 
  filter(group_structure == "h", `final_decision?` == "group") 
# => everyone in the hierarchichal condition agreed that the leader made the decision
```
# Third check: Perceived influence

## aggregations and calculation of average influence per group
```{r}
# average influence by participant
influence_check <- manip_checks %>% 
  group_by(group, group_structure, TMS) %>% 
  summarise(aggr_infl_p1 = mean(influence_p1), aggr_infl_p2 = mean(influence_p2), aggr_infl_p3 = mean(influence_p3))

View(influence_check)

# merge influence of three participants into one column 
influence_check <- influence_check %>% 
  gather('aggr_infl_p1', 'aggr_infl_p2', 'aggr_infl_p3', key = "participant", value = "aggr_infl")

# order 
influence_check <- influence_check %>% 
  arrange(group)

View(influence_check)

# calculate influence by group
influence_check <- influence_check %>% 
  group_by(group, group_structure, TMS) %>% 
  summarise(avg_influence = mean(aggr_infl, na.rm = TRUE), sd_avg_infl = sd(aggr_infl, na.rm = TRUE))
```
## calculate coefficient of variation => perceived influence disparity

```{r}
influence_check <- influence_check %>% 
  group_by(group, group_structure, TMS) %>%  
  mutate(coefficient_of_variation = sd_avg_infl/avg_influence)
```
## testing the difference between h and so

```{r}
library(coin)
# explore normality 
ggplot(data = influence_check, aes(coefficient_of_variation)) + geom_histogram(binwidth = .04) +
facet_wrap(~group_structure)

t.test(coefficient_of_variation ~ group_structure, alternative = "greater", data = influence_check) 
# one-tailed => signifikant, participants in the hierarchical condition perceived a higher discrepancy in influence

influence_check %>% 
  group_by(group_structure) %>% 
  summarise(sd = sd(coefficient_of_variation))

cohensD(coefficient_of_variation ~ group_structure, data = influence_check)

# change group structure and TMS to factors
influence_check <- influence_check %>% 
  ungroup()

View(influence_check)

influence_check <- mutate_at(influence_check, vars(group_structure, TMS), as.factor)

# given that the perceived influence disparity is not normally distributed, perform One-Way Permutation Test based on 9999 Monte-Carlo resamplings:

oneway_test(coefficient_of_variation ~ group_structure, data = influence_check, distribution = approximate(nresample = 9999)) 
# => still significant 
```
## testing the difference between TMS and noTMS

```{r}
t.test(coefficient_of_variation ~ TMS, data = influence_check) 
# two-tailed => not significant

oneway_test(coefficient_of_variation ~ TMS, data = influence_check, distribution = approximate(B = 9999)) 
# => still not significant
```
## testing for an effect of the TMS manipulation on the hierarchical manipulation

```{r}
# first, look at a potential interaction effect
summary(lm(coefficient_of_variation ~ group_structure * TMS, data=influence_check))

# second, test potential effect of TMS on group structure only within hierarchical groups
independence_of_manipulations <- influence_check %>% 
  filter(group_structure == "h")

t.test(coefficient_of_variation ~ TMS, data = independence_of_manipulations) 

# => neither the interaction nor the direct comparison of hierarchical_TMS with hierarchical_NoTMS are significant!! 
```
# Fourth check: Are leaders actually more powerful?

```{r}
# average influence by participant
leader_check <- manip_checks %>% 
  group_by(group, group_structure, TMS) %>% 
  mutate(infl = 
            case_when(
              id == 1  ~ mean(influence_p1),
              id == 2  ~ mean(influence_p2),
              id == 3  ~ mean(influence_p3)
            )
  )

t.test(infl ~ `leader?`, data=leader_check)

# average responsibility by participant
leader_check <- manip_checks %>% 
  group_by(group, group_structure, TMS) %>% 
  mutate(infl = case_when(
              id == 1  ~ mean(influence_p1),
              id == 2  ~ mean(influence_p2),
              id == 3  ~ mean(influence_p3)
            ),
         resp =  case_when(
              id == 1  ~ mean(respon_p1),
              id == 2  ~ mean(respon_p2),
              id == 3  ~ mean(respon_p3)
            )
  )

t.test(resp ~ `leader?`, data=leader_check)

View(leader_check)
```
# Fifth check: Perceived responsibility

## first aggregations and calculation of average influence per group
```{r}
# average responsibility by participant
responsibility_check <- manip_checks %>% 
  group_by(group, group_structure, TMS) %>% 
  summarise(aggr_resp_p1 = mean(respon_p1), aggr_resp_p2 = mean(respon_p2), aggr_resp_p3 = mean(respon_p3))

View(responsibility_check)

# collapse aggregated responsibility scores to create a single vector
responsibility_check <- responsibility_check %>% 
  gather('aggr_resp_p1', 'aggr_resp_p2', 'aggr_resp_p3', key = "participant", value = "avg_respon")

responsibility_check %>% 
  arrange(group)

# calculate mean and standard deviation of the average responsibility per group
responsibility_check <- responsibility_check %>% 
  group_by(group, group_structure, TMS) %>%
  summarise(responsibility = mean(avg_respon), sd_respon = sd(avg_respon))
  
# coefficient of variation for responsibility => perceived responsibility disparity
responsibility_check <- responsibility_check %>%
  group_by(group, group_structure, TMS) %>% 
  mutate(coefficient_respon = sd_respon/responsibility)
```
## testing for potential differences between "h" and "so" as well as "TMS" and "noTMS"

```{r}
# t-test 
responsibility_check <- responsibility_check %>% ungroup()
t.test(coefficient_respon ~ group_structure, alternative = "greater", data = responsibility_check)

cohensD(coefficient_respon ~ group_structure, data = responsibility_check)

# violation of normality?
describe(responsibility_check$coefficient_respon)
ggplot(responsibility_check, aes(coefficient_respon)) +
  geom_histogram(binwidth = 0.02)

# non-parametric test necessary, so first change character vectors to factors
responsibility_check <- responsibility_check %>% 
  ungroup()
  
responsibility_check <- mutate_at(responsibility_check, vars(group_structure, TMS), as.factor)

# finally test
oneway_test(coefficient_respon ~ group_structure, data = responsibility_check, distribution = approximate(B = 9999))

oneway_test(coefficient_respon ~ TMS, data = responsibility_check, distribution = approximate(B = 9999))         
```
# Sixth check: Explore differences in perceived overall responsibility and influence between h and so groups

```{r}
# violation of normality?
ggplot(responsibility_check, mapping = aes(responsibility)) +
  geom_histogram(binwidth = 0.25)

describe(responsibility_check$responsibility) 
# look at skew & kurtosis => it's fine

describe(influence_check$avg_influence) 
# seems fine, too

# test for significant difference
t.test(responsibility ~ group_structure, data = responsibility_check) 
# => There IS a SIGNIFICANT difference in perceived average responsibility

t.test(avg_influence ~ group_structure, data = influence_check) 
# => There is NO SIGNIFICANT difference in perceived average influence
```
# Manipulation check for TMS

```{r}
manip_checks %>% 
  filter(TMS == 'noTMS') %>% 
  filter(`exp_p1?` == 'correct' & `exp_p2?` == 'correct' & `exp_p3?` == 'correct') %>% 
  count()/120 * 100

```