---
title: "Memory Test Data"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Libraries

```{r}
library(readr)
library(tidyverse)
library(forcats)
library(psych)
```
# Data prep

```{r}
memory_test <- read_csv("data/memory_test_data.csv")
group_df <- read_csv("data/group_level_data.csv")
```
## drop groups to be excluded

```{r}
memory_test <- memory_test %>% 
  filter(!group %in% c(14, 80))

group_df <- group_df %>% 
  filter(!group %in% c(14, 80))
```
## create new shared data frame

```{r}
group_df <- group_df %>% 
  dplyr::select(group:duration_min) %>% 
  separate(condition, c('group_structure','TMS'), sep = "_", remove = FALSE, convert = TRUE) %>% 
  mutate(binary_decision = decision == "C") %>% 
  mutate(binary_decision_numeric = binary_decision * 1)

View(group_df)

joint_df <- memory_test %>% 
  left_join(group_df, by = "group")
```
## create variable for pieces of information that participants had learned per pilot 

```{r}
joint_df <- joint_df %>% 
  group_by(group, id, pilot) %>% 
  mutate(pos_information_learned_pilot = post_correct_pos - correct_same_pos, 
         neg_information_learned_pilot = post_correct_neg - correct_same_neg, 
         all_information_learned_pilot = pos_information_learned_pilot + neg_information_learned_pilot)
```
# Information gain

```{r}
info_gain_per_person <- joint_df %>% 
  group_by(group, id, group_structure, TMS, condition) %>% 
  summarise(info_learned = sum(all_information_learned_pilot)) 
  
info_gain <- info_gain_per_person %>% 
  group_by(group, group_structure, TMS, condition) %>% 
  summarise(info_learned_avg = mean(info_learned))

info_gain

## Does condition predict information gain?
summary(lm(info_learned ~ TMS * group_structure, data = info_gain_per_person))
summary(lm(info_learned_avg ~ TMS * group_structure, data = info_gain))

ggplot(data = info_gain, aes(condition, info_learned_avg)) +
  geom_bar(stat = "identity")
```
# Additionial manipulation check for TMS: Look whether in TMS condition, participants remembered more items about the pilot they were an expert on

## summarize pos. and neg. information remembered before discussion
```{r}
View(joint_df)

joint_df <- joint_df %>%
  group_by(group, id, pilot) %>% 
  mutate(correct_pre_count_pilot = pre_correct_neg + pre_count_pos)
```
## analyze TMS condition only

```{r}
# remove noTMS groups
TMS_only <- joint_df %>% 
  filter(TMS == "TMS") 

TMS_only %>% 
  dplyr::select(group, id, pilot, correct_pre_count_pilot)

TMS_short <- TMS_only %>% 
  group_by(group, id, pilot) %>% 
  mutate(exp_pilot = id == 1 & pilot == "A" | id == 2 & pilot =="B" | id == 3 & pilot == "C")

anova_mod <- aov(correct_pre_count_pilot ~ exp_pilot, data = TMS_short)
summary(anova_mod)
eta_sq(anova_mod)

TMS_short <- TMS_only %>% 
  group_by(id, pilot) %>% 
  summarise(avg_remembered = mean(correct_pre_count_pilot)) %>% 
  mutate(exp_pilot = id == 1 & pilot == "A" | id == 2 & pilot =="B" | id == 3 & pilot == "C")

summary(aov(avg_remembered ~ exp_pilot, data = TMS_short))
```
## vica versa: remove TMS gorups

```{r}
noTMS_only <- joint_df %>% 
  filter(TMS == "noTMS") 

noTMS_only %>% 
  dplyr::select(group, id, pilot, correct_pre_count_pilot) 

noTMS_short <- noTMS_only %>% 
  group_by(group, id, pilot) %>% 
  mutate(exp_pilot = id == 1 & pilot == "A" | id == 2 & pilot =="B" | id == 3 & pilot == "C")

anova_counter_mod <- aov(correct_pre_count_pilot ~ exp_pilot, data = noTMS_short)
summary(anova_counter_mod)
eta_sq(anova_counter_mod)
```

# Controlling for memory

## is memory itself a predictor for decision outcome?

```{r}
memory_as_predictor <- joint_df %>% 
  mutate(binary_decision = decision == "C") %>% 
  group_by(group, condition, TMS, group_structure, binary_decision) %>% 
  summarise(group_avg_pre_remembered = mean(correct_pre_count_pilot))

summary(glm(binary_decision ~ group_avg_pre_remembered, family = "binomial", data = memory_as_predictor))
```

